---
title: "p8105_hw5_nh2796"
output: github_document
date: "2024-11-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(broom)
library(purrr)
```

# Problem 1

```{r}
simulate_birthdays <- function(n) {
  birthdays <- sample(1:365, n, replace = TRUE)
  return(length(birthdays) > length(unique(birthdays)))
}
```

```{r}
set.seed(1)
probabilities <- numeric(49)

for (n in 2:50) {
  results <- numeric(10000)
  for (i in 1:10000) {
    results[i] <- simulate_birthdays(n)
  }
  probabilities[n - 1] <- mean(results)
}
```

```{r}
data <- data.frame(group_size = 2:50, probability = probabilities)
ggplot(data, aes(x = group_size, y = probability)) + 
  geom_line() + 
  labs(x = "Group Size", y = "Probability of Shared Birthday")
```


# Problem 2

**Initial Setup**

```{r}
n <- 30
sigma <- 5
mu_values <- 0:6
num_simulations <- 5000
alpha <- 0.05
```

**Function**

```{r}
simulate_power <- function(mu, n, sigma, num_simulations, alpha) {
  results <- replicate(num_simulations, {
    x <- rnorm(n, mean = mu, sd = sigma)
    t_test <- t.test(x, mu = 0)
    tidy_result <- broom::tidy(t_test)
    tibble(
      estimate = tidy_result[["estimate"]],
      p_value = tidy_result[["p.value"]]
    )
  }, simplify = FALSE) %>% bind_rows()
 
   results <- results %>%
    mutate(null_rejected = p_value < alpha)
  
   return(results)
}
```

```{r}
sim_results <- map_dfr(mu_values, function(mu) {
  data <- simulate_power(mu, n, sigma, num_simulations, alpha)
  data %>% mutate(mu_true = mu)
})
```


```{r}
power_summary <- sim_results %>%
  group_by(mu_true) %>%
  summarize(
    power = mean(null_rejected),
    avg_estimate = mean(estimate),
    avg_estimate_rejected = mean(estimate[null_rejected])
  )
```
 
**plots**
```{r}
power_summary %>%
  ggplot(aes(x = mu_true, y = power)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Power vs Effect Size",
    x = "True Mean (µ)",
    y = "Power"
  ) +
  theme_minimal()
```

```{r}
power_summary %>%
  ggplot(aes(x = mu_true)) +
  geom_line(aes(y = avg_estimate, color = "All Samples")) +
  geom_line(aes(y = avg_estimate_rejected, color = "Null Rejected")) +
  labs(
    title = "Average Estimate of µ vs. true µ",
    x = "True Mean (µ)",
    y = "Average Estimate",
    color = "Group"
  ) +
  theme_minimal()
```
  
# **Problem 3**

**Data Import**

```{r}
homicide_data =
  read.csv("./homicide-data.csv")
```
Description of raw data: This data set has information on homicides from 50 large US cities. It includes information about each victim's first and last name, race/ethnicity, age, sex, the city that the homicide occured, the state that it occured, latitude and longitude, and the disposition of the case which indicates if the case was closed or if an arrest was made. 

```{r}
homicide_data = 
  homicide_data %>%
  mutate(city_state = paste(city, state, sep = ", "))
```

```{r}
homicide_summary =
  homicide_data %>%
  group_by(city_state) %>%
  summarise(total_homicides = n(), 
            unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest")))
```
# Prop test part 1
```{r}

baltimore_prop_test <- prop.test(
  x = homicide_summary %>% filter(city_state == "Baltimore, MD") %>% pull(unsolved_homicides),
  n = homicide_summary %>% filter(city_state == "Baltimore, MD") %>% pull(total_homicides)
)

baltimore_tidy <- broom::tidy(baltimore_prop_test) %>% 
  select(estimate, conf.low, conf.high)
```

# proptest part 2
```{r}
prop_test_new <- homicide_summary %>% 
  mutate(
    results_prop = map2(unsolved_homicides, total_homicides, ~prop.test(.x, .y))
  ) %>% 
  mutate(results_tidy = map(results_prop, broom::tidy)) %>% 
  unnest(results_tidy) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


# Plot
```{r}
ggplot(prop_test_new, aes(x = reorder(city_state, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() + 
  labs(
    x = "City", 
    y = "Proportion of Unsolved Homicides",
    title = "Proportion of Unsolved Homicides by City"
  ) +
  theme_minimal()
```

